\documentclass [a4paper, 12pt] {article}
\usepackage[frenchb, english]{babel}
\usepackage {lmodern, textcomp}
\usepackage {graphicx}
\usepackage {array}
\usepackage {geometry}

\usepackage{enumitem}
\setlist[description]{leftmargin=\parindent,labelindent=\parindent}

\newcolumntype{M}[1]{>{\raggedright}m{#1}}
\newcolumntype{N}{>{\global\let\currentrowstyle\relax}}
\newcolumntype{^}{>{\currentrowstyle}}
\newcommand{\rowstyle}[1]{\gdef\currentrowstyle{#1}%
    #1\ignorespaces
}

\newcommand \projectname {\mbox{\bsc{Academi-co}}}
\newcommand \teamname {\mbox{\bsc{SoftAware}}}
\newcommand \teammeber {Petr \bsc{Binko}, Nicolas \bsc{Cotte}, Selim \bsc{Selimi}, Ka\"\i ko \bsc{Goren}, Aslam \bsc{Cader}}


\begin {document}

\title {\projectname \, Vision}
\author {\teamname}
\date{\today}

\maketitle
\begin{abstract}
% Petr \bsc{Binko}, Nicolas \bsc{Cotte}, Selim \bsc{Selimi}, Ka\"\i ko \bsc{Goren}, Aslam \bsc{Cader}
% \bigskip
\begin{table}[h]
\caption{Revision History}
\begin{tabular}{| N l | ^ l | ^ M{6cm} | ^ M{4cm} |}
	\hline
	\rowstyle{\bfseries} Date & Version & Description & Author \tabularnewline
	\hline \hline
	19/03/2018 & 1.0 & First draft & \teamname \ Team \tabularnewline
	\hline
\end{tabular}
\end{table}
\end{abstract}

\newpage
\tableofcontents
\newpage

\section{Introduction}
\subsection{Purpose}
This document aims to clarify the motivations and objectives behind the \projectname \ project.

\subsection{Scope}
This document will be used as a reference as to what is expected from the \projectname \ project and the \teamname \ team.

\subsection{Definitions, Acronyms, and Abbreviations}
\begin{description}
	\item [User:] Any user of the website (visitor or registered)
	\item [Visitor:] User who did not create an account
	\item [Registered user:] User who created an account (free or premium)
	\item [Free user:] User who created a free account
	\item [Premium user:] User who created a paying account
	\item [Moderator:] Trusted user with special authorizations and tools to regulate the content
	\item [Administrator:] Person responsible for website maintenance
	\item [Client:] Website owner
\end{description}

\subsection{References}


\subsection{Overview}
This document details the product?s standing in the context of the current market, its stakeholders and foreseen users, its features and other specifications as well as its constraints and other requirements. It also better defines the project in regards to its priorities, planning and risks.



\section{Positioning}
\subsection{Business Opportunity}
\projectname \ is a unique idea, taking a pre-existing and proven model and applying it to a whole new and more global purpose, effectively reaching a large untapped market. The monetization opportunities it offers are both numerous and flexible.

\subsection{Problem Statement}
\begin{tabular}{| M{6cm} | M{8cm} |}
	\hline
	The problem is & a lack of means of communication between students and potential helpers \tabularnewline
	\hline
	that affects & university students and teachers \tabularnewline
	\hline
	the impact of which is & a whole sector of potential customers, waiting for better means of communication \tabularnewline
	\hline
	a successful solution would be & a web service providing easy and accessible means of fast communication, with a focus and incentivisation on mutual assistance \tabularnewline
	\hline
\end{tabular}

\subsection{Product Position Statement}
\begin{tabular}{| M{3cm} | M{11cm} |}
	\hline
	For & students and teachers in universities \tabularnewline
	\hline
	who & need easy and efficient communication means \tabularnewline
	\hline
	\projectname & is a forum-like web service \tabularnewline
	\hline
	that & provides tools to facilitate communication and help \tabularnewline
	\hline
	unlike & StackExchange. \tabularnewline
	\hline
	Our product & is for general academic purpose, instead of focusing on one specific domain \tabularnewline
	\hline
\end{tabular}



\section{Stakeholder and User Descriptions}
\subsection{Market Demographics}
Our target demographic is academic students and teachers and especially the students, which are mostly a young demographic, completely versed in the use of modern web-based technology. The usefulness of the service should bring a rapid increase in the number of users and, with that, multiple non-intrusive monetization opportunities, like add banners. Those have been a proven steady source of income that typically bodes well with that type of public, as multiple sites (like youtube.com) can attest.

\subsection{Stakeholder Summary}
\begin{tabular}{| M{2.5cm} | M{5.5cm} | M{6cm} |}
	\hline
	Name & Description & Responsibilities \tabularnewline
	\hline \hline
	Student & Student who needs or can give help & Brings new content to the service (questions/answers). \\ Communicates about the product and brings new users.
\tabularnewline
	\hline
	Teacher & Teacher that wants to interact with students to help them and share various content with them & Brings new content to the service by answering the students and sharing useful documents/information \tabularnewline
	\hline
	Client & Buyer of the product & Provides funding and resources for the product and benefits from its long-term monetary opportunities \tabularnewline
	\hline
	Administrator & Person who will be in charge of the service's maintenance & Keeps the system running and up to date \tabularnewline
	\hline
\end{tabular}

\subsection{User Summary}
\begin{tabular}{| M{2.5cm} | M{5.5cm} | M{6cm} |}
	\hline
	Name & Description & Responsibilities \tabularnewline
	\hline \hline
	Connected User & Interacts to ask and answer questions &
	\begin{itemize}
		\item Creates threads
		\item Posts answers to threads
		\item Shares information
	\end{itemize}
	\tabularnewline
	\hline
	Premium User & Interacts to ask and answer questions, and gets additional tools (e.g custom tags and document sharing) &
	\begin{itemize}
		\item Creates threads
		\item Posts answers to threads
		\item Shares documents/information
		\item Can create custom tags
	\end{itemize} \tabularnewline
	\hline
	Visitor & Someone that needs information that has been already discussed by Connected Users &
	\begin{itemize}
		\item See other peoples' posts
	\end{itemize} \tabularnewline
	\hline
	Moderator & A volunteer user who maintains order in the forum &
	\begin{itemize}
		\item Moderate posts/comments
		\item Creates threads
		\item Posts answers to threads
		\item Shares information
	\end{itemize} \tabularnewline
	\hline
\end{tabular}

\subsection{User Environment}
Web-based application accessed through a browser on computers, tablets and smartphones.

\subsection{Stakeholder Profiles}
\subsubsection{Student}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & University student in any kind of academic field \tabularnewline
	\hline
	Type & A casual user, experienced in the use of web-based applications \tabularnewline
	\hline
	Responsibilities &
	\begin{itemize}
		\item Producing content
		\item Relaying information about the service (word of mouth)
	\end{itemize} \tabularnewline
	\hline
	Success Criteria &
	\begin{itemize}
		\item Able to easily find answers to his questions
		\item Help the others
	\end{itemize} \tabularnewline
	\hline
	Involvement & Is the main user \tabularnewline
	\hline
	Deliverables & None \tabularnewline
	\hline
\end{tabular}

\subsubsection{Teacher}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & University teacher in any kind of academic field \tabularnewline
	\hline
	Type & A casual user, experienced in the use of web-based applications \tabularnewline
	\hline
	Responsibilities &
	\begin{itemize}
		\item Producing content
		\item Relaying information about the service (word of mouth)
	\end{itemize} \tabularnewline
	\hline
	Success Criteria & Able to easily deliver answers to student's questions \tabularnewline
	\hline
	Involvement & Is a user \tabularnewline
	\hline
	Deliverables & None \tabularnewline
	\hline
\end{tabular}

\subsubsection{Client}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Financial contributor \tabularnewline
	\hline
	Type & Business executive \tabularnewline
	\hline
	Responsibilities & Provides financial support \tabularnewline
	\hline
	Success Criteria & Obtained a reliable source of income through optimal monetization techniques \tabularnewline
	\hline
	Involvement & Main executive authority behind the project \tabularnewline
	\hline
	Deliverables & None \tabularnewline
	\hline
\end{tabular}

\subsubsection{Administrator}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Website maintainer
	\begin{itemize}
		\item Website maintainer
		\item Gives moderator rights
	\end{itemize} \tabularnewline
	\hline
	Type & IT Expert \tabularnewline
	\hline
	Responsibilities &
	\begin{itemize}
		\item Maintains the website
		\item Solves potential future website issues
	\end{itemize} \tabularnewline
	\hline
	Success Criteria & A working and easy to maintain website \tabularnewline
	\hline
	Involvement & Is the person to contact if there are any maintenance problems \tabularnewline
	\hline
	Deliverables & Product's documentation \tabularnewline
	\hline
\end{tabular}

\subsection{User Profiles}
\subsubsection{Registered Premium User}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Registered premium (paying) user \tabularnewline
	\hline
	Type & Casual user \tabularnewline
	\hline
	Responsibilities &
	\begin{itemize}
		\item Producing content
		\item Relaying information about the service (word of mouth)
	\end{itemize} \tabularnewline
	\hline
	Success Criteria &
	\begin{itemize}
		\item Able to easily find answers to his questions
		\item Help the others
	\end{itemize} \tabularnewline
	\hline
	Involvement & None \tabularnewline
	\hline
	Deliverables & Additional features (e.g creating custom tags, managing threads with own tags) \tabularnewline
	\hline
\end{tabular}

\subsubsection{Registered Free User}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Registered user with a free account \tabularnewline
	\hline
	Type & Casual user \tabularnewline
	\hline
	Responsibilities &
	\begin{itemize}
		\item Producing content
		\item Relaying information about the service (word of mouth)
	\end{itemize} \tabularnewline
	\hline
	Success Criteria &
	\begin{itemize}
		\item Able to easily find answers to his questions
		\item Help the others
	\end{itemize} \tabularnewline
	\hline
	Involvement & None \tabularnewline
	\hline
	Deliverables & None \tabularnewline
	\hline
\end{tabular}

\subsubsection{Visitor}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Unregistered (anonymous) user \tabularnewline
	\hline
	Type & Casual user \tabularnewline
	\hline
	Responsibilities & None \tabularnewline
	\hline
	Success Criteria & Able to easily find answers to his questions \tabularnewline
	\hline
	Involvement & None \tabularnewline
	\hline
	Deliverables & None \tabularnewline
	\hline
\end{tabular}

\subsubsection{Moderator}
\begin{tabular}{| >{\bfseries} M{4cm} | M{10cm} |}
	\hline
	Description & Registered user chosen to become a moderator \tabularnewline
	\hline
	Type & Trustworthy user, experienced with forums \tabularnewline
	\hline
	Responsibilities & Ensures the proper functioning of the administrative policies \tabularnewline
	\hline
	Success Criteria &
	\begin{itemize}
		\item Able to easily find answers to his questions
		\item Help the others
		\item Able to moderate posts/comments
	\end{itemize} \tabularnewline
 \tabularnewline
	\hline
	Involvement & Makes sure that the policies and guidelines of the website are respected by the casual users \tabularnewline
	\hline
	Deliverables & Moderating tools \tabularnewline
	\hline
\end{tabular}

\subsection{Key Stakeholder or User Needs}
\begin{tabular}{| N M{2cm} | ^ l | ^ M{2cm} | ^ M{4cm} | ^ M{3cm} |}
	\hline
	\rowstyle{\bfseries} Need & Priority & Concerns & Current Solution & Proposed Solutions \tabularnewline
	\hline \hline
	Get help on specific topic & 1 & Students and teachers & Find a specialized site or an available person & Global and centralized forum for academic questions \tabularnewline
	\hline
	Discuss academic subjects & 2 & Students and teachers & Use social networks or contacts to find interested persons & Create and find threads on that subject with tags \tabularnewline
	\hline
\end{tabular}

\subsection{Alternatives and Competition}
\subsubsection{StackExchange}
Big userbase, wide range of subjects

\subsubsection{StackOverflow}
Big userbase with steadily and quickly available help.

\subsubsection{Social Media}
Social media (Facebook, Twitter, Google+, etc.) - Global and easy to use.



\section{Product Overview}
\subsection{Product Perspective}
\projectname \ is a standalone web-based product.

\subsection{Summary of Capabilities}
\begin{tabular}{| N M{7cm} | ^ M{7cm} |}
	\hline
	\rowstyle{\bfseries} Stakeholders Benefit & Supporting Features \tabularnewline
	\hline \hline
	Students can easily and efficiently find help for their problems & Threads creation and tag based search \tabularnewline
	\hline
	Paying customers get easy tools for sharing knowledge & Uploading documents, creating custom tags \tabularnewline
	\hline
	Client can flexibly monetize the site & Advertisement banners on the website and premium accounts \tabularnewline
	\hline
\end{tabular}

\subsection{Assumptions and Dependencies}
\projectname \ is a standalone web-based product, working on different browsers (Firefox, Chrome, Safari, Internet Explorer, Edge).

% \subsection{Cost and Pricing}
% \subsection{Licensing and Installation}



\section{Product Features}
\subsection{Create an Account}
As a user, I want to securely create an account, so that I can post on the website.

\subsection{Post}
As a registered user, I want to create threads and answer existing ones, so that I can ask for help or help others.

\subsection{Visualize}
As a user, I want to read ergonomically presented threads, so that I can get answers in a digestible way.

\subsection{Search}
As a user, I want to search on the website, so that I can easily find and visualize existing threads and look for a specific user.

\subsection{Login/Logout}
As a registered user, I want to login and logout to the website, so that I can post.

\subsection{Homepage}
As a user, I want to be brought to a quality interface when opening the website, so that I get an easy and immediate access to the site's core content.

\subsection{Voting System}
As a registered user, I want to rate threads and answers, so that other users may find the content I deemed most useful.

\subsection{Content Organization}
As a user, I want to see the most useful content in priority, so that I increase my chances of finding what I am looking for.

\subsection{Tags}
As a user, I want to have subjects-related tags, so that I can identify the content's topics.

\subsection{Inbox}
As a user, I want to have a private inbox, so that I can receive private messages and notifications.

\subsection{Add Administrator}
As the super-user or an administrator, I want to add new administrators, so that the website can be maintained.

\subsection{Send Candidacy for Moderation}
As a user, I want to apply for a moderator position, so that it can be reviewed by administrators and I can participate to maintaining the website's content.

\subsection{Elect Moderator}
As an administrator, I want to pick candidate moderators and revoke their privileges, so that the website content's integrity can be maintained.

\subsection{Moderation Tools}
As a moderator, I want to have intuitive moderation tools, so that I can enforce the website's guidelines and filter inappropriate content.

\subsection{Metadata}
As a user, I want to access information about the content, so that I can get a better idea of its context.

\subsection{Create a Premium Account}
As a user, I want to create a premium account, so that I can get additional tools on the website.

\subsection{Create a Custom Tag}
As a premium user, I want to create custom tags, so that posts related to my topic can be found easily.

\subsection{Advertisement Banners}
As a client, I want to put advertisement banners on the site's pages, so that I can efficiently and non-intrusively monetize the website.

\subsection{Help Page}
As a user, I want to be informed about the site's guidelines and tools, so that I can use the site optimally.

\subsection{Flag}
As a registered user, I want to signal inappropriate content, so that it can be reviewed by a moderator.

\subsection{Format}
As a registered user, I want to have access to tools to format my posts, so that they can be more interactive and easy to read.

\subsection{Dashboard}
As a registered user, I want to have a dedicated page, so that I can access content relevant to my interests.

\subsection{Upload Documents}
As a premium user, I want to upload documents, so that I can share documents



\section{Constraints}
Must be compatible with popular web browsers (Firefox, Chrome, Safari, Internet Explorer, Microsoft Edge).



\section{Quality Ranges}
\begin{description}
	\item [Maintainability:] the website must be easy to maintain and update;
	\item [Performance:] the site must be responsive and the search functionalities must be fast;
	\item [Availability:] the site must be available at all times from every major web browser, except during scheduled maintenance tasks;
	\item [Robustness:] the content added to the site must be durably stored;
	\item [Usability:] the site must be intuitive to use;
	\item [Modifiability:] the site can support the addition of new languages;
	\item [Scalability:] the site must support a progressive but large increase of its userbase (workload/storage).
\end{description}



\section{Precedence and Priority}
\begin{itemize}
		\item Create account
		\item Login / logout
		\item Post
		\item Visualize
		\item Tags
		\item Search
		\item Voting system
		\item Content organization
		\item Homepage
		\item Create premium account
		\item Advertisement banners
		\item Inbox
		\item Add administrator
		\item Send candidacy for moderation
		\item Elect moderators
		\item Moderation tools
		\item Metadata
		\item Dashboard
		\item Flags
		\item Help page
		\item Upload documents
		\item Create custom tag
		\item Format
\end{itemize}



\section{Other Product Requirements}
\subsection{Applicable Standards}
Compatibility with common web browsers.

\subsection{System Requirements}
An internet connection and a web browser.

% \subsection{Performance Requirements}
% \subsection{Environmental Requirements}



\section{Documentation Requirements}
\subsection{User Manual}
None

\subsection{Online Help}
Help page (cf. specifications)

\subsection{Installation Guides, Configuration, and Read Me File}
None



\section{Planning}
cf. planning visualization



\section{Risks}
\begin{tabular}{| N l | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} |}
	\hline
	\rowstyle{\bfseries} Priority & Description & Impact on the project & Occurrence indicator & Mitigation strategy & Alternative plan \tabularnewline
	\hline \hline
	1 & Lack of experience from the development team & Buggy or missing features, delays & Spending longer than expected on researching tools, bugs and integration problems & Use external knowledge bases (Google, Stefan, Steve) & Reassign workload, abandon/simplify requirement \tabularnewline
	\hline
	2 & Too many new requirements appearing during development & Delays & User story analysis reveals new requirements more than once & Analyze each user story thoroughly at the start of the project, adjust planning accordingly & Simplify vision of the impacted features, scale down requirements \tabularnewline
	\hline
\end{tabular}
	
\begin{tabular}{| N l | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} |}
	\hline
	\rowstyle{\bfseries} Priority & Description & Impact on the project & Occurrence indicator & Mitigation strategy & Alternative plan \tabularnewline
	\hline \hline
	3 & Bad planning management & Dependency issues, missing features & Missing dependencies when starting a task & Regular planning/ dependencies review & Rework the project planning, and work reassignment \tabularnewline
	\hline
	4 & Bad development time management (can be caused by external factors) & Delays & Missing feedback form the developer, being increasingly behind personal schedule & Expect longer work days than planned & Work reassignment \tabularnewline
	\hline
	5 & Unforeseen browser compatibility issues & Delays, sections of the site unsupported on certain browsers & Encountering compatibility issues that were not accounted for during development & Very regular testing and team prepared to encounter and tackle such problems & Simplify the visuals/features causing the problem on the impacted browsers \tabularnewline
	\hline
	6 & Lack of developers availability & Delays, missing features & Developers regularly unable to attend meetings and/or deliver their work & Flexible plannings and obtaining commitment & Review scope and redistribute work \tabularnewline
	\hline
\end{tabular}
	
\begin{tabular}{| N l | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} | ^ M{2cm} | ^ M{2.3cm} |}
	\hline
	\rowstyle{\bfseries} Priority & Description & Impact on the project & Occurrence indicator & Mitigation strategy & Alternative plan \tabularnewline
	\hline \hline
	7 & Lack of appeal from the site & Loss in userbase and potential revenue & Insufficient growth in the userbase during a benchmark period & Get feedback on the site from potential users and graphic design specialists & Rework the site's appearance and add incentives for user activities \tabularnewline
	\hline
\end{tabular}



\end {document}
